---
title: "Introduction to smartPARE"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{my-vignette}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

<br>
Hej Hej 1

<br>


```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```



# Installation

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.align="center", 
  warning=FALSE, 
  message=FALSE, 
  idy.opts=list(width.cutoff=120))
library(smartPARE)
```

<br>
Hej Hej
<br>


## Heading 2
### Heading 3

--------
********

* Bulleted list
* Item 2
    * Nested bullets need a 4-space indent.
    * Item 2b
    
  * It's possible to put multiple paragraphs of text in a list item. 

    But to do that, the second and subsequent paragraphs must be
    indented by four or more spaces. It looks better if the first
    bullet is also indented.

Definition
  : a statement of the exact meaning of a word, especially in a dictionary.

_italic_ or *italic*
__bold__ or **bold**    
[link text](destination)
<http://this-is-a-raw-url.com>

| Right | Left | Default | Center |
|------:|:-----|---------|:------:|
|   12  |  12  |    12   |    12  |
|  123  |  123 |   123   |   123  |
|    1  |    1 |     1   |     1  |


knitr::kable(data.frame())

`code`

```
# A comment
add <- function(a, b) a + b
```

```c
int add(int a, int b) {
  return a + b;
}
```

```{r}
# Add two numbers together
add <- function(a, b) a + b
add(10, 20)
```

```r
# Add two numbers together
add <- function(a, b) a + b
add(10, 20)
## [1] 30
```

```{r, results = "asis"}
pander::pandoc.table(iris[1:3, 1:4])
```
